### 2020-10-12 thesis/msc-thesis.tex
Verbesserungen vorgeschlagen von Thomas

\subsection{Example(s) of CSS Problems Today}
\begin{enumerate}
     \item CSS incomplete in governmental administration
           \begin{enumerate}
                \item identity card renewal
                \item change of home address
                \item change of residency status
           \end{enumerate}

     \item CSS incomplete in universities
           \begin{enumerate}
                \item transfer of profile: grades, certificates, etc. between universities
                \item applications in general (study place, semester abroad, ...)
           \end{enumerate}

     \item CSS different for each enterprise / organization
           \begin{enumerate}
                \item multiple identities
                \item multiple profiles => addresses, phone numbers, mail address
                \item time consuming to manage same information in all systems
           \end{enumerate}
\end{enumerate}

\subsection{Solution for CSS Problems}
\begin{enumerate}
     \item One CSS providing company, which integrates multiple / all EA
     \item One identity, profile, address, phone number, location, ...
     \item Easy management of identity used by multiple enterprises / organizations
\end{enumerate}

\subsection{Integration necessity}
\begin{enumerate}
     \item Each enterprise / organization has its own identities, profiles, etc. in multiple systems
     \item The CSS providing company needs to manage those systems / data of each enterprise / organization
     \item Enterprise Integration solves this Problem
\end{enumerate}

@@

\subsection{Integration Challenges}
\begin{enumerate}
     \item Heterogeneous Enterprise Architecture Systems
           \begin{enumerate}
                \item Different Applications
                \item Different Application Vendors
                \item Different / No Application Interfaces
                \item Legacy Systems
           \end{enumerate}

@@

\subsection{Presented Solutions}
\begin{enumerate}
     \item Messaging Integration
           \begin{enumerate}
                \item Loose Coupling
                      \begin{enumerate}
                           \item Loose Coupling simplifies adaption to changing EA => simpler Maintenance
                           \item Loose Coupling simplifies integration of new EA systems => integration of heterogeneous EA
                           \item Loose Coupling allows Reuse of "Modules" => faster development
                      \end{enumerate}

                \item Messaging enables communication with many systems through Adapters

                \item Messaging provides mechanisms for Stability
                      \begin{enumerate}
                           \item Store-and-Forward
                           \item Load Balancing
                      \end{enumerate}

     \item Integration Patterns
           \begin{enumerate}
                \item Patterns speed up construction of Integration Architecture
                \item Patterns are proven solutions
                \item Patterns abstract from concrete technologies
                      \begin{enumerate}
                           \item Simplifies understanding of integration concept
                           \item Allows implementation with different technologies
                      \end{enumerate}

@@

\section{Customer Self-Service}

\subsection{Definition}
\begin{enumerate}
     \item Definition in the context of the thesis
\end{enumerate}

\subsection{Documentation}
\begin{enumerate}
     \item How can CSS-Scenarios be documented?
\end{enumerate}

\subsection{List of Scenarios}

\subsection{Purpose in Thesis}
\begin{enumerate}
     \item Finding relevant EAPs
     \item Requirement analysis of business Connector
     \item Interface definition of business connector
\end{enumerate}

\section{Architecture Patterns}
\subsection{Definition}
\begin{enumerate}
     \item Definition
     \item Metadata
     \item Views
     \item Architecture bricks
     \item Data bricks
     \item Business processes
\end{enumerate}

\subsection{Purpose in Thesis}
\begin{enumerate}
     \item Basis for real-life enterprise architectures
     \item Provides architecture and data bricks the integration can build up on
\end{enumerate}

\subsection{Architecture- and Data bricks}
\begin{enumerate}
     \item Description of EAPs used in the thesis
     \item Reasons why each EAP is relevant for CSS
           \begin{enumerate}
                \item Derived by comparing CSS-Scenarios with business processes
           \end{enumerate}
     \item Architecture bricks and data bricks of EAPs relevant for CSS-Scenarios
     \item Documentation of resulting Architecture and data bricks
\end{enumerate}

\subsection{Requirements of Enterprise Architecture}
\begin{enumerate}
     \item List of requirements towards the integration Architecture
           \begin{enumerate}
                \item Adapters for systems
                \item Required Format of incoming data
           \end{enumerate}
\end{enumerate}

\section{Business Connector}

\subsection{Definition}
\begin{enumerate}
     \item Provides functionality of "external" service provider
     \item Purpose is to simplify integration
     \item Can be assumed to provide sufficient interfaces
\end{enumerate}

\subsection{Purpose in Thesis}
\begin{enumerate}
     \item Provides interface for CSS functionalities
     \item Should be integrated in architecture and data bricks
\end{enumerate}

\subsection{Documentation}
\begin{enumerate}
     \item How to document the business Connector in this context

     \item List of provided functionalities along with their interfaces
           \begin{enumerate}
                \item Derived from CSS-Scenarios
                \item Derived from IDAS Connector
           \end{enumerate}

@@

\section{Integration Patterns}

\subsection{Definition}
\begin{enumerate}
     \item Messaging Methodology
     \item Patterns describe often solved messaging problems
\end{enumerate}

\subsection{Purpose in Thesis}
\begin{enumerate}
     \item Already explained in Motivation?
\end{enumerate}

\subsection{Patterns used in Thesis}
\begin{enumerate}
     \item Description of Patterns later used in the integration architecture
\end{enumerate}

@@

\chapter{My contribution}

@@

@@

\section{Operating Manual}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Experimental evaluation}

\section{Customer Landscape}

\section{Customer Requirements}

\section{Integration}

\subsection{Using the Operating Manual}

\subsection{Relevant Bricks}

\subsubsection{Data Bricks}

\subsubsection{Architecture Bricks}

\subsection{Resulting Integration}

\subsubsection{Integration Documentation}

\section{Evaluation}

\subsection{Satisfaction of Requirements}

\subsubsection{Enterprise Architecture Requirements}

\subsubsection{Customer Requirements}

\subsubsection{Business Connector Requirements}

\subsubsection{Integration Architecture Requirements}

\subsection{Resource-Heaviness}

\subsubsection{Required time for application}

\subsubsection{Size of Resulting System}

\subsubsection{Increasing cost due to scaling}

>>>>

\subsection{Evolution of digital Customer Self-Service}
\begin{enumerate}
     \item Increasing consumer standards
           \begin{enumerate}
                \item Passwordless sign in
                \item instant updates
           \end{enumerate}

     \item New regulations
           \begin{enumerate}
                \item DSGVO
                \item Onlinezugangsgesetz
                \item DVG (eAU, eRezept)
                \item psd2
           \end{enumerate}

\subsection{CSS as a Service}
\begin{enumerate}
     \item Enterprises can offer CSS service, satisfying modern requirements and regulations
\end{enumerate}

\subsection{Service Integration}
\begin{enumerate}
     \item The provided CSS service has to be integrated into existing enterprise architecture
\end{enumerate}

@@

Solution for integration challenges
\begin{enumerate}
     \item Heterogeneous Enterprise Architecture Systems
           \begin{enumerate}
                \item Different Applications
                \item Different Application Vendors
                \item Different / No Application Interfaces
                \item Legacy Systems
           \end{enumerate}

@@

@@

\section{Customer Self-Service}
\begin{enumerate}
     \item Definition in the context of the thesis
     \item Purpose in Thesis
     \item Overview of CSS-Scenarios found in literature
\end{enumerate}

\section{Architecture Patterns}
\begin{enumerate}
     \item Definition
     \item Purpose in Thesis
     \item Explanation of used Patterns
\end{enumerate}

\subsection{Business Connector}
\begin{enumerate}
     \item Definition in context of the thesis
     \item Purpose in Thesis
\end{enumerate}

\section{Messaging Patterns}
\begin{enumerate}
     \item Definition
     \item Messaging
           \begin{enumerate}
                \item Answer: Why is messaging used?
           \end{enumerate}
     \item Patterns
           \begin{enumerate}
                \item Answer: Why are patterns used?
           \end{enumerate}
     \item Explanation of used patterns
\end{enumerate}

\chapter{Groundwork}

\subsection{CSS-Scenarios}
\begin{enumerate}
     \item Categorization of Scenarios
     \item Combining similar scenarios (into a more general one)
     \item Prioritization
     \item ToDo: How to document?
     \item Documentation of final list
\end{enumerate}

\subsection{Enterprise Architecture}
\begin{enumerate}
     \item Architecture- and Data bricks
           \begin{enumerate}
                \item Selection of EAPs relevant for CSS
                      \begin{enumerate}
                           \item Derived by comparing CSS-Scenarios with business processes
                      \end{enumerate}
                \item Evaluation of Architecture bricks and data bricks of EAPs relevant for CSS-Scenarios
                \item Documentation of resulting Architecture and data bricks
           \end{enumerate}

     \item Requirements of Enterprise Architecture
           \begin{enumerate}
                \item List of requirements towards the integration Architecture
                      \begin{enumerate}
                           \item Adapters for systems
                           \item Required Format of incoming data
                      \end{enumerate}
           \end{enumerate}
\end{enumerate}

\section{Business Connector}
\begin{enumerate}
     \item How to document the business Connector
     \item List of provided functionalities along with their interfaces
           \begin{enumerate}
                \item Derived from CSS-Scenarios
                \item Derived from IDAS Connector
           \end{enumerate}

@@

@@

\chapter{Integration Architecture}

@@

\begin{enumerate}
     \item Requirements of Enterprise Architecture
     \item Requirements of Business Connector
     \item Requirements of Integration System
\end{enumerate}

@@

\chapter{Evaluation}

\section{Technological Evaluation}

\subsection{Available Messaging Technologies}

\subsection{Implementation of Integration Architecture}

\subsection{Evaluation of result}

\section{Experimental Evaluation}

\subsection{Customer Example}

\subsection{Application of Integration Architecture}

\subsection{Evaluation of result}

\section{Operation Manual}
\begin{enumerate}
     \item Guide on how to implement and deploy the integration architecture
     \item incorporates results of previous evaluations
\end{enumerate}
